\documentclass[a4paper, 10pt]{article}

\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{siunitx}
\usepackage{cleveref}
\usepackage{mathtools}
\usepackage{graphicx}

\usepackage{xcolor}
\definecolor{cA}{HTML}{0072BD}
\definecolor{cB}{HTML}{EDB120}
\definecolor{cC}{HTML}{77AC30}
\definecolor{cD}{HTML}{D95319}

\newcommand{\tA}[1]{\textcolor{cA}{#1}}
\newcommand{\tB}[1]{\textcolor{cB}{#1}}
\newcommand{\tC}[1]{\textcolor{cC}{#1}}
\newcommand{\tD}[1]{\textcolor{cD}{#1}}

\newtheorem{theorem}{Theorem}
\crefname{theorem}{Thm.}{Thms.}

\begin{document}

\title{Sample document}
\author{hari64boli64}
\date{\today}
\maketitle

\section{LLAlignAnd}

\begin{table}[h]
    \centering
    \begin{tabular}{lll}
        \&=              &
        $\begin{aligned}
                 a & = b \\
                 c & = d
             \end{aligned}$ &
        \tA{ok}            \\[0.3cm]
        =\&              &
        $\begin{aligned}
                 a = & b \\
                 c = & d
             \end{aligned}$ &
        \tD{ng}            \\[0.3cm]
        =\{\}\&          &
        $\begin{aligned}
                 a = {} & b \\
                 c = {} & d
             \end{aligned}$ &
        \tA{ok}
    \end{tabular}
\end{table}

\section{LLColonEqq}

\begin{table}[h]
    \centering
    \begin{tabular}{lll}
        x := y                   & $x := y$        & \tD{ng} \\
        x $\backslash$coloneqq y & $x \coloneqq y$ & \tA{ok} \\
        x ::= y                  & $x ::= y$       & \tD{ng} \\
        x $\backslash$Coloneqq y & $x \Coloneqq y$ & \tA{ok}
    \end{tabular}
\end{table}

\section{LLCref}

\begin{theorem}
    \label{thm:sample}
    This is a sample theorem.
\end{theorem}

Use \cref{thm:sample} instead of Theorem~\ref{thm:sample}.

\section{LLDoubleQuotation}

Use ``XXX'' instead of “XXX” or "XXX".

\section{LLENDash}

\begin{itemize}
    \item Erdos-Renyi (random graph, Erd\H{o}s--R\'enyi)
    \item Einstein-Podolsky-Rosen (quantum mechanics, Einstein--Podolsky--Rosen)
    \item Fruchterman-Reingold (graph drawing, Fruchterman--Reingold)
    \item Gauss-Legendre (numerical integration, Gauss--Legendre)
    \item Gibbs-Helmholtz (thermodynamics, Gibbs--Helmholtz)
    \item Karush-Kuhn-Tucker (optimization, Karush--Kuhn--Tucker)
\end{itemize}

Exception: Fritz-John (optimization, name of a person)

False Positive: Wrong-Example

\section{LLNonASCII}

 {　}！＂＃＄％＆＇（）＊＋，－．／

日本語の文章は、upLaTeXでフツウに書けます。

(You can write Japanese sentences as usual with upLaTeX.)

\section{LLSI}

Example: 10 KB, $3.5\mathrm{MiB}$, \SI{500}{\giga\byte}.

\newcommand{\EB}{Some Awesome Command.This is not ExaByte.}

\EB.

This 1EB is one ExaByte.

\section{LLT}

\begin{equation*}
    X^T \quad X^\top \quad X^{\mathsf{T}}
\end{equation*}

\section{LLTitle}

\subsection{non title case words}

\subsubsection{
    This Is a Correct Title
}

\subparagraph{SubParagraph: Test With Ref~\ref{thm:sample}}

\section{LLUserDefined}

I want to use $\mathrm{a}$ instead of $a$ for superscript.

\begin{equation*}
    f^a(X) \quad f^{\mathrm{a}}(X)
\end{equation*}

\end{document}

